An Authoritative Adventure

### 2022-10-27 article.tex
Fixed table colour for tables from Basic Rules
Added example showing how to split a table across the column.

@@

\begin{table*}[b]%
  \begin{DndTable}[width=\linewidth,header=Colors Supported by This Package]{lX}
    \textbf{Color}                  & \textbf{Description} \\
    \rowcolor{PhbLightGreen}
    |PhbLightGreen|                 & Light green used in PHB Part 1 (Default) \\
    \rowcolor{PhbLightCyan}
    |PhbLightCyan|                  & Light cyan used in PHB Part 2 \\
    \rowcolor{PhbMauve}
    |PhbMauve|                      & Pale purple used in PHB Part 3 \\
    \rowcolor{PhbTan}
    |PhbTan|                        & Light brown used in PHB appendix \\
    \rowcolor{DmgLavender}
    |DmgLavender|                   & Pale purple used in DMG Part 1 \\
    \rowcolor{DmgCoral}
    |DmgCoral|                      & Orange-pink used in DMG Part 2 \\
    \rowcolor{DmgSlateGray}
    |DmgSlateGray| (|DmgSlateGrey|) & Blue-gray used in DMG Part 3 \\
    \rowcolor{DmgLilac}
    |DmgLilac|                      & Purple-gray used in DMG appendix \\
    \rowcolor{BrGreen}
    |BrGreen|                       & Gray-green used for tables in Basic Rules\\
  \end{DndTable}
\end{table*}

>>>>

\subsection{Split Tables}
Temporarily adding a column using |multicols| can
be used to achieve the effect of a split column
table.

Add the following around two or more tables (note
the non-breaking space character (\char`\~) used for
the table header on all but the first):

\begin{lstlisting}[basicstyle=\ttfamily\small]
\begin{multicols}{2}
\begin{DndAltTable}[header=Encounters]{cX}
...
\end{DndAltTable}
\begin{DndAltTable}[header=~]{cX}
...
\end{DndAltTable}
\end{multicols}
\end{lstlisting}

This achieves the following effect:

\begin{multicols}{2}
\begin{DndAltTable}[header=Encounters]{cX}
    \textbf{d10} & \textbf{Encounter} \\
    1  & Toppled statue \\
    2  & Ferocious kitten \\
    3  & Broken sign \\
    4  & Blind beggar \\
    5  & Piercing wail \\
\end{DndAltTable}
\begin{DndAltTable}[header=~]{cX}
    \textbf{d10} & \textbf{Encounter} \\
    6  & Pack of wolves \\
    7  & Drunk owlbear \\
    8  & Freed prisoners \\
    9  & Wild magic zone \\
    10 & Magic item \\
\end{DndAltTable}
\end{multicols}

@@

\begin{table*}[b]%
  \begin{DndTable}[width=\linewidth,header=Colors Supported by This Package]{lX}
    \textbf{Color}                  & \textbf{Description} \\
    \rowcolor{PhbLightGreen}
    |PhbLightGreen|                 & Light green used in PHB Part 1 (Default) \\
    \rowcolor{PhbLightCyan}
    |PhbLightCyan|                  & Light cyan used in PHB Part 2 \\
    \rowcolor{PhbMauve}
    |PhbMauve|                      & Pale purple used in PHB Part 3 \\
    \rowcolor{PhbTan}
    |PhbTan|                        & Light brown used in PHB appendix \\
    \rowcolor{DmgLavender}
    |DmgLavender|                   & Pale purple used in DMG Part 1 \\
    \rowcolor{DmgCoral}
    |DmgCoral|                      & Orange-pink used in DMG Part 2 \\
    \rowcolor{DmgSlateGray}
    |DmgSlateGray| (|DmgSlateGrey|) & Blue-gray used in DMG Part 3 \\
    \rowcolor{DmgLilac}
    |DmgLilac|                      & Purple-gray used in DMG appendix \\
    \rowcolor{BrGreen}
    |BrGreen|                       & Light-gray used for tables in Basic Rules\\
  \end{DndTable}
\end{table*}
